Scientific Report - Summary of Research\\ Ambizione: ``Automatized compilation of sequential software to a diverse set of hardware accelerators''\\ Grant number: PZ00P2 168016\\ Period: 01.05.2018– 31.12.2020\\ Grantee: Tobias Grosser\\ \today

### 2021-04-21 paper.tex
deploy: f3f3a37fddb759f036af733bb2113981a3629546
Add papers under submission
Publications
Increase font size
deploy: 855bc6b4a322191e61cc2a64e993c3a940da4331

\ifx\paperversion\paperversiondraft
  \documentclass[manuscript,\review anonymous]{acmart}
\fi

@@

\ifx\paperversion\paperversioncamera
  \documentclass[manuscript, nonacm, natbib]{acmart}\settopmatter{}
\fi

@@

@@

\subsection{Publications (published)}
\begin{itemize}
	\item \bibentry{chelini2021mlir}
	\item \bibentry{10.1145/3437801.3441613}
	\item \bibentry{grosser2020fast}
	\item \bibentry{chelini2020automatic}
	\item \bibentry{khan2020polyhedral}
	\item \bibentry{schueki2020llhd}
	\item \bibentry{kurth2020mixed}
	\item \bibentry{kourtis2020compiling}
\end{itemize}
\subsection{Publications (accepted)}
\subsection{Publications (under review)}
\subsection{Publications (in preparation)}
\begin{itemize}
	\item \bibentry{gysi2020ooc}
\end{itemize}

>>>>

\ifx\paperversion\paperversiondraft
  \documentclass[11pt, manuscript,\review anonymous]{acmart}
\fi

@@

\ifx\paperversion\paperversioncamera
  \documentclass[11pt, manuscript, nonacm, natbib]{acmart}\settopmatter{}
\fi

@@

The primary goals of this Ambizione research project were proposed as:
\begin{itemize}
\item Develop a multi-target heterogeneous compute compiler for C++ and Julia code that generates binaries which effectively exploit
OpenCL-capable accelerators including GPU, Xeon-Phi, and FPGA.
\item Research new techniques to scale polyhedral optimization to large kernels and to improve their efficiency to a level that permits
the effective exploration of a large set of mapping choices.
\item Derive effective performance models based on hybrid analytical/machine-learning techniques and use them to analyze and optimize accelerator mapping decisions in a large body of existing software.
\item Evolve our new performance modeling techniques to work within the resource constraints of Julias dynamic run-time system and use Julia to experiment with distributed learning techniques.
\end{itemize}

The focus of year three in this Ambizione project was move our polyhedral core
infrastructure into real-world compilers such as MLIR and improve its
performance. In addition, we worked on establishing backend abstractions for 
dral techniques. In the
following, we discuss four milestones we identified as important to reach these goals:
1. Fast, robust, and (provably?) correct polyhedral libraries
2. Solid polyhedral compiler infrastructure
• Modular pattern-based optimizations for CPU and GPU systems
• DeLICM: Scalar dependence removal
3. Precise cache models for fully-associative caches
4. Domain-specific optimization for climate science
The following two goals from year one remain important:
1. Solidify and formalize our underlying models
2. Effective accelerator offloading for large-scale programs

@@

\subsection{Publications (published)}
\begin{itemize}
	\item \bibentry{chelini2021mlir}
	\item \bibentry{10.1145/3437801.3441613}
	\item \bibentry{grosser2020fast}
	\item \bibentry{chelini2020automatic}
	\item \bibentry{khan2020polyhedral}
	\item \bibentry{schueki2020llhd}
	\item \bibentry{kurth2020mixed}
	\item \bibentry{kourtis2020compiling}
\end{itemize}
\subsection{Publications (under review)}
\begin{itemize}
	\item \bibentry{gysi2020ooc}
	\item \bibentry{fehr2021}
	\item \bibentry{anurudth2021}
	\item \bibentry{theo2021}
	\item \bibentry{pichanatan2021}
	\item \bibentry{copic2021}
\end{itemize}
